---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MetroSystemEval

The goal of MetroSystemEval is to simplify the running of the R code for King County Metro's System Evaluation. The functions in this package produce standard route level metrics for all periods of the day and all days of the week and require GTFS files for Metro's current and future networks.

## Installation

You can install the development version of MetroSystemEval from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("melissa-gaughan/MetroSystemEval")
```

## Example

You can call the  create_route_metrics() function on any GTFS that you have on your computer. You need to supply a file path (make sure to switch back slashes to forward slashes!) as well as determine whether the GTFS represents current or future service. You also need to provide a date for the start of the service change in "YYYY-MM-DD" format:

```{r example, eval=FALSE}
library(MetroSystemEval)
example_route_metric_table <- create_route_metrics(gtfs_type = "current", gtfs_path = fs::path_package("extdata", "233_gtfs.zip", package = "MetroSystemEval"),
                                  service_change_start_date ="2023-09-02")
View(example_route_metric_table)
```
